### 2018-03-08 project.tex
weekly update

@@

@@

>>>>

	\begin{proof}
	By definition if $K_1$ and $K_2$ are compact then for each $\mathcal{U}_1$ and $\mathcal{U}_2$ of $K_1$ and $K_2$ such that $\bigcup \mathcal{U}_1 = K_1$ and $\bigcup \mathcal{U}_2 = K_2$. So, $\bigcup (\mathcal{U}_1 \cup \mathcal{U}_2) = K_1 \cup K_2$. Let $K_3 = K_1 \cup K_2$ and $\mathcal{U}_3 = \mathcal{U}_1 \cup \mathcal{U}_2$. Then for $K_3$ there exists $\mathcal{U}_3$ such that $\bigcup \mathcal{U}_3 = K_3$. \newline Also by definition there must exist $\mathcal{F}_1$ and $\mathcal{F}_2$ such that $\mathcal{F}_1, \mathcal{F}_2 \subseteq \mathcal{U}_1, \mathcal{U}_2$ respectively. Then, $\mathcal{F}_1$ and $\mathcal{F}_2 \subseteq \mathcal{U}_1 \cup \mathcal{U}_2$. Let $\mathcal{F}_3 = \mathcal{F}_1 \cup \mathcal{F}_2$, then $\mathcal{F}_3 \subseteq \mathcal{U}_3$. Now observe that $\bigcup \mathcal{F}_1 = K_1$ and $\bigcup \mathcal{F}_2 = K_2$. The $\bigcup (\mathcal{F}_1 \cup \mathcal{F}_2 ) = K_1 \cup K_2$ and $\bigcup \mathcal{F}_3 = K_1 \cup K_2$ so $K_1 \cup K_2$ must be compact.
	\end{proof}

@@

	\begin{proof}

	A subset $K$ of space $\mathbb{X}$ is compact if for every open cover $\mathcal{U}$ of $K$ there exists $\mathcal{F} \subseteq \mathcal{U}$ such that $\bigcup \mathcal{F} = K$.\newline Let $K \subseteq \mathbb{X}$, let $\mathcal{U} = \lbrace (a, b) : a < b \in K \rbrace$ then $\bigcup \mathcal{U} = K$. Let $\mathcal{F} = \lbrace F : F = U \in \mathcal{U} \rbrace$, then $\bigcup \mathcal{F} = \bigcup \mathcal{U} = K$, so $\bigcup \mathcal{F} = K$.

	\end{proof}

@@

	\begin{proof}

	Assume $K$ is compact, then for all $\mathcal{U}$ of $K$, $\bigcup \mathcal{U} = K$. Now we find $\mathcal{F} \subseteq \mathcal{U}$ that also covers $K$. For $\bigcup \mathcal{U} = K$, then $0, 1 \in \bigcup \mathcal{U}$. Let $\mathbb{A} = \bigcap \lbrace (\frac{-1}{n}, \frac{1}{n}) : n \in \mathbb{Z}^+ \rbrace$ and let $\mathbb{C} = \lbrace \frac{1}{n} : n \in \mathbb{Z}^+$. So $\mathbb{A} \subseteq \mathcal{U}$ and $\mathbb{C} \subseteq \mathcal{U}$ so $\mathbb{A} \cup \mathbb{C} \subseteq \mathcal{U}$, let $\mathcal{F} = \mathbb{A} \cup \mathbb{C}$, then $\bigcup \mathcal{F} = \bigcup( \lbrace 0 \rbrace \cup \lbrace \frac{1}{n} : n \in \mathbb{Z}^+ \rbrace)$ so $\bigcup \mathcal{F} = K$.

	\end{proof}
